---
title: "Super Awesome Project Template"
output: word_document
date: "2025-04-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Rules
Starting Cash
- Every player begins with $1,500 to start, and once you're out of liquid cash you lose.
Standard dice roll
- Player moves forward the number of spaces shown on two six sided dice. 
Rolling doubles
- Player rolls doubles (same number on both dice) and gets another turn. 
Three consecutive doubles
- If a player rolls doubles three times in a row, they go directly to jail. 
Passing Go
- If a player passes "Go" they collect $200 from the bank.
Chance Cards
- Certain board spaces have chance cards on them which instruct the player to move to a different space, or pay/earn money. They can send players to jail, Go, or various properties. 
Community Chest Cards
- Certain board spaces have community chest cards on them which instruct the player to move to a different space, pay/earn money, or get out of jail free card. 
Go to jail space
- Landing on "Go to jail" space sends the player directly to jail without collecting $200.
In jail movement
- the player can roll doubles to get out of jail, use the "get out of jail free" card, or pay $50. 
Buying/Landing on properties
- When you land on a property that hasn't been bought already, you are able to buy it if desired. If you land on a property that another player owns, you have to pay them an amount based on the property and houses on it. 
## Luke Olson

```{r, binwidth=8, binheight=8}
#2. Let's Get Moving

library(tidyverse)


#Creating the board
monopoly_board = tibble(position = 0:39, space = c("Go", "Mediterranean Avenue", "Community Chest", "Baltic Avenue", "Income Tax", "Reading Railroad", "Oriental Avenue", "Chance", "Vermont Avenue", "Connecticut Avenue", "Jail / Just Visiting", "St. Charles Place", "Electric Company", "States Avenue", "Virginia Avenue", "Pennsylvania Railroad", "St. James Place", "Community Chest", "Tennessee Avenue", "New York Avenue", "Free Parking", "Kentucky Avenue", "Chance", "Indiana Avenue", "Illinois Avenue", "B&O Railroad", "Atlantic Avenue", "Ventnor Avenue", "Water Works", "Marvin Gardens", "Go to Jail", "Pacific Avenue", "North Carolina Avenue", "Community Chest", "Pennsylvania Avenue", "Short Line Railroad", "Chance", "Park Place", "Luxury Tax", "Boardwalk"))

# Define color group by property (not included is Chance, Community Chest, Income Tax, Luxury Tax, Go, Go to Jail, and Jail/ Just Visiting)
property_colors = tribble(~space,                    ~color_group,
                          "Mediterranean Avenue",   "Brown",
                          "Baltic Avenue",          "Brown",
                          "Oriental Avenue",        "Light Blue",
                          "Vermont Avenue",         "Light Blue",
                          "Connecticut Avenue",     "Light Blue",
                          "St. Charles Place",      "Pink",
                          "States Avenue",          "Pink",
                          "Virginia Avenue",        "Pink",
                          "St. James Place",        "Orange",
                          "Tennessee Avenue",       "Orange",
                          "New York Avenue",        "Orange",
                          "Kentucky Avenue",        "Red",
                          "Indiana Avenue",         "Red",
                          "Illinois Avenue",        "Red",
                          "Atlantic Avenue",        "Yellow",
                          "Ventnor Avenue",         "Yellow",
                          "Marvin Gardens",         "Yellow",
                          "Pacific Avenue",         "Green",
                          "North Carolina Avenue",  "Green",
                          "Pennsylvania Avenue",    "Green",
                          "Park Place",             "Dark Blue",
                          "Boardwalk",              "Dark Blue",
                          "Reading Railroad",       "Black",
                          "Pennsylvania Railroad",  "Black",
                          "B&O Railroad",           "Black",
                          "Short Line Railroad",    "Black",
                          "Water Works",            "Purple",
                          "Electric Company",       "Purple")



# Join colors into board data
monopoly_board = monopoly_board %>%
  left_join(property_colors, by = "space") %>%
  mutate(color_group = replace_na(color_group, "Other"))


# Assign colors (exact Monopoly-themed colors)
monopoly_colors = c("Brown" = "#8B4513", "Light Blue" = "#ADD8E6", "Pink" = "#FF69B4", "Orange" = "#FFA500", "Red" = "#FF0000", "Yellow" = "#FFD700", "Green" = "#008000", "Dark Blue" = "#00008B", "Black"= "black", "Purple" ="purple", "Other" = "grey")


# Begin the movement around the board
simulate_player = function(turns = 1000) {
  position = 0
  landed = integer(turns)
  
  for (i in 1:turns) {
    roll = sample(1:6, 1) + sample(1:6, 1)  # The sum of two six-sided dice
    position = (position + roll) %% 40     # starts back at 0 when you make it past "GO"
    landed[i] <- position
  }
  return(landed)
}


# Include 4 players
set.seed(25)  # Useful so others get the same output. Can put any number in here and will get varying outcomes. 
n_players = 4
turns_per_player = 1000
all_positions = map(1:n_players, ~simulate_player(turns_per_player)) %>% unlist() %>% as_tibble() %>% rename(position = value)



#Visualization
#save the Count as landings and order them by which were landed on most out of 4 players having 1000 turns each
landings = all_positions %>% count(position, name = "landed_on") %>% left_join(monopoly_board, by = "position") %>% arrange(desc(landed_on))  %>% mutate(label = paste(space, position), label = factor(label, levels = label[order(landed_on)]))


#Create the plot based on how frequently each space was landed on using the monopoly colors as well for an easier visualization. 
ggplot(landings, aes(x = label, y = landed_on, fill = color_group)) +
  geom_col() +
  scale_fill_manual(values = monopoly_colors)+
  coord_flip() +
  labs(title = "Most Frequently Landed On Monopoly Spaces", x = "Board Space", y = "Number of Landings") +
  theme_minimal(base_size = 10)


```


## Owen Schuler

```{r student2}

```


## Caden Rummel


```{r student3}

```



## Landen Frye

```{r student4}
2+2
```
