---
title: "Monopoly Final Project"
author: "Landen Frye, Caden Rummel, Luke Olson, Owen Schuler"
output: word_document
date: "2025-05-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



1. Rules
    Starting Cash
- Every player begins with $1,500 to start, and once you're out of liquid cash you lose.
    Standard dice roll
- Player moves forward the number of spaces shown on two six sided dice. 
    Rolling doubles
- Player rolls doubles (same number on both dice) and gets another turn. 
    Three consecutive doubles
- If a player rolls doubles three times in a row, they go directly to jail. 
    Passing Go
- If a player passes "Go" they collect $200 from the bank.
    Chance Cards
- Certain board spaces have chance cards on them which instruct the player to move to a different space, or pay/earn money. They can send players to jail, Go, or various properties. 
    Community Chest Cards
- Certain board spaces have community chest cards on them which instruct the player to move to a different space, pay/earn money, or get out of jail free card. 
    Go to jail space
- Landing on "Go to jail" space sends the player directly to jail without collecting $200.
    In jail movement
- the player can roll doubles to get out of jail, use the "get out of jail free" card, or pay $50.
    Free Parking
- All money that is paid to the bank goes to free parking. If a player lands on this space, they receive all money that the free parking "account" has collected. This is not initially done, it is done at the end to compare play length before and after. 
    Mortgages
- Mortgages are not a part of this simulation as it was deemed too complicated. If a player runs out of money, the player that eliminated them gets the properties.

    Buying/Landing on properties
- When you land on a property that hasn't been bought already, you are able to buy it if desired. If you land on a property that another player owns, you have to pay them an amount based on the property and houses on it. 



2. Which properties are landed on most frequently?
```{r, echo=FALSE}

#Creates a data frame with the position, name, type of space, and corresponding color
monopoly_board <- data.frame(
  Position = 0:39,
  Name = c(
    "GO", "Mediterranean Avenue", "Community Chest", "Baltic Avenue", "Income Tax", "Reading Railroad", "Oriental Avenue", "Chance", "Vermont Avenue", "Connecticut Avenue", "Jail / Just Visiting", "St. Charles Place", "Electric Company", "States Avenue", "Virginia Avenue", "Pennsylvania Railroad", "St. James Place", "Community Chest", "Tennessee Avenue", "New York Avenue", "Free Parking", "Kentucky Avenue", "Chance", "Indiana Avenue", "Illinois Avenue", "B&O Railroad", "Atlantic Avenue", "Ventnor Avenue", "Water Works", "Marvin Gardens", "Go To Jail", "Pacific Avenue", "North Carolina Avenue", "Community Chest", "Pennsylvania Avenue", "Short Line", "Chance", "Park Place", "Luxury Tax", "Boardwalk"),
  Type = c(
    "Go", "Property", "Community Chest", "Property", "Income Tax", "Railroad", "Property", "Chance", "Property", "Property", "Jail", "Property", "Utility", "Property", "Property", "Railroad", "Property", "Community Chest", "Property", "Property", "Free Parking", "Property", "Chance", "Property", "Property", "Railroad", "Property", "Property", "Utility", "Property", "Go To Jail", "Property", "Property", "Community Chest", "Property", "Railroad", "Chance", "Property", "Luxury Tax", "Property"),
  Color = c(
    "Other", "Brown", "Other", "Brown", "Other", "Black", "Light Blue", "Other", "Light Blue", "Light Blue", "Other", "Pink", "Purple", "Pink", "Pink", "Black", "Orange", "Other", "Orange", "Orange", "Other", "Red", "Other", "Red", "Red", "Black", "Yellow", "Yellow", "Purple", "Yellow", "Other", "Green", "Green", "Other", "Green", "Black", "Other", "Dark Blue", "Other", "Dark Blue"),
  stringsAsFactors = FALSE)

#colors used for graphs later
monopoly_colors = c("Brown" = "#8B4513", "Light Blue" = "#ADD8E6", "Pink" = "#FF69B4", "Orange" = "#FFA500", "Red" = "#FF0000", "Yellow" = "#FFD700", "Green" = "#008000", "Dark Blue" = "#00008B", "Black"= "black", "Purple" ="purple", "Other" = "grey")



#Basic simulation movement based only on dice rolls
simulate_basic <- function(players = 4, turns = 1000) {
#makes player positions
  positions <- rep(0, players)
#tracks how many times each space is visited
  visits <- rep(0, 40)

#rolls two dice and then moves the player while counting each visit
  for (turn in 1:turns) {
    for (player in 1:players) {
      move <- sum(sample(1:6, 2, replace = TRUE))
      positions[player] <- (positions[player] + move) %% 40
      visits[positions[player] + 1] <- visits[positions[player] + 1] + 1
    }                      # +1 thing is needed because r doesnt like starting a vector at 0
  }

#combines visit counts with board data
  visits_df <- monopoly_board
  visits_df$Visits <- visits #adds this column to dataframe when function is ran
  return(visits_df)
}

library(ggplot2)

#plots the basic simulation
basic_results <- simulate_basic()


#Visualization of it
ggplot(basic_results, aes(x = reorder(Name, Position), y = Visits, fill = Color)) +
  geom_col() +
  scale_fill_manual(values = monopoly_colors) +
  labs(title = "Basic Monopoly Most Common Spaces",
       x = "Board Space", y = "Visits") +
  theme(axis.text.x = element_text(angle = 90, size = 7), 
        plot.title = element_text(hjust = 0.5))
```

Analysis for monopoly most common spaces without jail, doubles or chance: 

From a sample of 4 players each having 1000 turns, we found that without any rules and just using basic movement around the board there isn’t a significant difference between the number of times each space was landed on. Most spaces are hovering around 100 times being landed on. In the chart it seems like chance and community chest are landed on significantly more often, but this is because there are 3 of each on the board, thus explaining why they are landed on roughly 3 times as much as the other spaces. Besides this, there is pretty uniform distribution with each space having about a 2.5% or 1/40 chance of being landed on by a player. 


3. Improve your system to incorporate going to jail, including the doubles-rolling condition. Which properties are landed on most frequently now?
```{r, echo=FALSE}
#simulations with jail and rolling doubles
simulate_with_jail <- function(players = 4, turns = 1000) {
  positions <- rep(0, players)
  visits <- rep(0, 40)
#track jail status got this from chatgpt
  in_jail <- rep(FALSE, players)
#tracks turns spent in jail
  jail_turns <- rep(0, players)
  
  for (turn in 1:turns) {  #had chat help with this too
    for (player in 1:players) {
      doubles_count <- 0
      repeat {
        if (in_jail[player]) {
          jail_turns[player] <- jail_turns[player] + 1
          roll <- sample(1:6, 2, replace = TRUE)
          if (roll[1] == roll[2] || jail_turns[player] == 3) {
            #Leave jail if double is rolled or after 3 turns
            in_jail[player] <- FALSE
            jail_turns[player] <- 0
            move <- sum(roll)
          } else {
            break
          }
        } else {

        #Checks for doubles on rolls
          roll <- sample(1:6, 2, replace = TRUE)
          move <- sum(roll) #move across board based on sum of roll
          if (roll[1] == roll[2]) { #consecutive double system
            doubles_count <- doubles_count + 1
          } else {
            doubles_count <- 0
          }
            #goes to jail after rolling 3 doubles
          if (doubles_count == 3) {
            positions[player] <- 10
            in_jail[player] <- TRUE
            jail_turns[player] <- 0
            visits[11] <- visits[11] + 1 #counts 3 doubles in a row as a visit to jail
            break
          }
        }

        positions[player] <- (positions[player] + move) %% 40
        pos <- positions[player] + 1 

        #Landed on "Go To Jail" and counts as well
        if (monopoly_board$Type[pos] == "Go To Jail") {
          visits[31] <- visits[31] + 1 #counts as go to jail visit
          positions[player] <- 10
          in_jail[player] <- TRUE
          jail_turns[player] <- 0 #starts jail_turns system
          visits[11] <- visits[11] + 1 #counts as jail visit as well
        } else {
          visits[pos] <- visits[pos] + 1 #if not go to jail, count as normal
        }

        if (roll[1] != roll[2] || in_jail[player]) break
      }
    }
  }
  
  visits_df <- monopoly_board
  visits_df$Visits <- visits #same as above
  return(visits_df)
}

#plots jail simulation
jail_results <- simulate_with_jail() 

ggplot(jail_results, aes(x = reorder(Name, Position), y = Visits, fill = Color)) +
  geom_col() +
  scale_fill_manual(values = monopoly_colors) +
  labs(title = "Most Common Spaces with Jail and Doubles",
       x = "Board Space", y = "Visits") +
  theme(axis.text.x = element_text(angle = 90, size = 7), 
        plot.title = element_text(hjust = 0.5))
```

Analysis for monopoly most common spaces with jail and doubles: 

From a sample of 4 players each having 1000 turns, there is only a significant difference for spots landed on for just visiting/jail and a minor increase in chance / colors directly after jail. This is expected because the jail function was added and when a player lands on the go to jail space, it also counts a visit to the jail/just/visiting space. In essence, this makes it twice as likely that a player will land on the jail space when they go around the board. With chance being 7 spaces after jail, it makes it the most likely spot to land after going to jail, which would explain the increase in that.  The colors following jail also saw a minor increase, and that would be because the player is spending more time over there in the grand scheme of things. 


4. Incorporate the movement cards into your system. You can ignore the effects of non-movement cards, but not their existence! Which properties are landed on most frequently now?
```{r, echo=FALSE}
#adds movement effect for Chance cards
chance_movements <- c("GO" = 0, "Illinois Avenue" = 24, "St. Charles Place" = 11,
                      "Boardwalk" = 39, "Jail" = 10, "Back 3 Spaces" = -3) 
#all of the movement spaces from chance cards

#function that randomly draws a Chance card and applies its movement effect
draw_chance <- function(current_pos) {
  card <- sample(names(chance_movements), 1)
  if (card == "Back 3 Spaces") {
    return((current_pos - 3) %% 40)
  }
  return(chance_movements[card])
}
#Simulation with jail, doubles, and Chance card effects
simulate_with_chance <- function(players = 4, turns = 1000) {
  positions <- rep(0, players)
  visits <- rep(0, 40)
  in_jail <- rep(FALSE, players)
  jail_turns <- rep(0, players)
#finds which spaces are "Chance"
  chance_spaces <- which(monopoly_board$Type == "Chance")
  
  for (turn in 1:turns) {
    for (player in 1:players) {
      doubles_count <- 0
      repeat {
        if (in_jail[player]) {
        #uses the jail rules and applies it
          jail_turns[player] <- jail_turns[player] + 1 
          roll <- sample(1:6, 2, replace = TRUE) #explained above
          if (roll[1] == roll[2] || jail_turns[player] == 3) {
            in_jail[player] <- FALSE
            jail_turns[player] <- 0
            move <- sum(roll)
          } else break
        } else {
            #normal movement
          roll <- sample(1:6, 2, replace = TRUE)
          move <- sum(roll)
          if (roll[1] == roll[2]) {
            doubles_count <- doubles_count + 1
          } else {
            doubles_count <- 0
          }
          if (doubles_count == 3) {
            positions[player] <- 10
            in_jail[player] <- TRUE
            jail_turns[player] <- 0
            visits[11] <- visits[11] + 1
            break
          }
        }

        positions[player] <- (positions[player] + move) %% 40
        pos <- positions[player] + 1
        
        if (monopoly_board$Type[pos] == "Go To Jail") {
          visits[31] <- visits[31] + 1
          positions[player] <- 10
          in_jail[player] <- TRUE
          jail_turns[player] <- 0
          visits[11] <- visits[11] + 1
        } else if (pos %in% chance_spaces) {
          visits[23] <- visits[23] + 1
            #Landed on a Chance space
          new_pos <- draw_chance(positions[player])
          positions[player] <- new_pos
          visits[new_pos + 1] <- visits[new_pos + 1] + 1
        } else {
          visits[pos] <- visits[pos] + 1
        }

        if (roll[1] != roll[2] || in_jail[player]) break
      }
    }
  }

  visits_df <- monopoly_board
  visits_df$Visits <- visits
  return(visits_df)
}

#Plots full simulation with Chance cards incorporated
chance_results <- simulate_with_chance()
# Run and visualize
ggplot(chance_results, aes(x = reorder(Name, Position), y = Visits, fill = Color)) +
  geom_col() +
  scale_fill_manual(values = monopoly_colors) +
  labs(title = "Most Common Spaces with Everything",
       x = "Board Space", y = "Visits") +
  theme(axis.text.x = element_text(angle = 90, size = 7),
        plot.title = element_text(hjust = 0.5))

# summary_visits <- chance_results[order(-chance_results$Visits), c("Position", "Name", "Visits")]
# didnt need at the end

# print(summary_visits) didnt need this at the end

```
 
Analysis for monopoly most common spaces with jail, doubles, and chance: 

From a sample of 4 players each having 1000 turns while including jail and double rules along with chance cards, we found that there is only a noticeable difference in amount landed in the jail space and the places chance moves a player to.  The reason the jail space is higher is because of the “Go to Jail” space that automatically brings the player to the jail space along with the chance card that brings a player there, and because of the time spent in jail trying to roll to get out. The reason random spaces throughout the board are higher is due to the chance card bringing them there. If you look you will notice that GO, Illinois Avenue, St. Charles Place, and Boardwalk are the highest four excluding the jail, chance, and community chest spaces. This is due to the chance card having a chance of bringing a player to one of those spots, making it higher than most other spaces. A nuance made because of the jail space is seen 7-9 spaces after the jail space, where there is a slight uptick in the number of times landed. Because of the times landed on jail, it only makes sense that the spaces with an average two dice roll distance from jail should also see an increase in times landed on compared to the other spaces on the board.  


```{r, echo=FALSE}
library(dplyr)
library(knitr)

players <- 4
turns <- 1000
total_player_turns <- players * turns

# Add total + average visits to each board space
chance_results <- chance_results %>%
  mutate(AveragePerPlayerTurn = round(Visits / total_player_turns, 4))
summary_table <- chance_results %>%
  select(Position, Name, Visits, AveragePerPlayerTurn) %>%
  arrange(desc(Visits))

# Show as nice table
library(knitr)
# kable(summary_table, digits = 4) #got this from chatgpt, didnt need in final report
ggplot(chance_results, aes(x = reorder(Name, Position), y = AveragePerPlayerTurn, fill = Color)) +
  geom_col() +
  scale_fill_manual(values = monopoly_colors) +
  geom_text(aes(label = round(AveragePerPlayerTurn, 4)), 
            vjust = -0.3, size = 3, angle = 90) +
  labs(title = "Average Visits per Player Turn With Everything",
       x = "Board Space", y = "Avg Visits per Player Turn") +
  theme(axis.text.x = element_text(angle = 90, size = 7),
        plot.title = element_text(hjust = 0.5))
```
```{r, echo=FALSE}
expected_visits <- rep(sum(chance_results$Visits) / 40, 40)  # Uniform expectation
observed_visits <- chance_results$Visits

# Run chi-squared test
chisq_test <- chisq.test(x = observed_visits, p = rep(1/40, 40))

# Output test results
print(chisq_test) #didnt want in final report
chance_results$Expected <- expected_visits
chance_results$Deviation <- chance_results$Visits - expected_visits
chance_results$StdResidual <- (chance_results$Visits - expected_visits) / sqrt(expected_visits)

# Sort by standardized residuals
chance_results %>%
  arrange(desc(abs(StdResidual))) %>%
  select(Name, Visits, Expected, Deviation, StdResidual) %>%
  head(10)
  # kable(digits = 2)
```

```{r, echo=FALSE}
#this is without buying properties and whatnot
simulate_economy_game <- function(players = 4, max_turns = 4000) {
  set.seed(2)

  positions <- rep(0, players) #position system
  money <- rep(1500, players) #1500 starting money amount
  eliminated <- rep(FALSE, players) #stops having players in game if eliminated
  turns_alive <- rep(0, players) #counts number of turns a player has played

  log <- data.frame(Turn = integer(), Player = integer(), Action = character(), Money = numeric())

  for (turn in 1:max_turns) {
    for (player in 1:players) {
      if (eliminated[player]) next #if a player has been eliminated, go to next player

      # Move the player
      roll <- sum(sample(1:6, 2, replace = TRUE))
      new_position <- (positions[player] + roll) %% 40
      positions[player] <- new_position
      pos <- new_position + 1
      space <- monopoly_board$Name[pos]
      space_type <- monopoly_board$Type[pos]
      
      
     
       action <- "" #gives an empty string to describe what the player did during the turn, such as paid tax, collected go, etc
       
      # Handle money effects
      change <- 0 #amount of money a player gains or loses each turn, starts at 0 and changes based on what happened during the turn
       if (space_type == "Luxury Tax") {
       change <- -100
       action <- "Paid Luxury Tax"
      } else if (space_type == "Go") { #Made it so that you only got money if you landed on go in an effort to control the money in the game, otherwise there was no chance to feasibly lose enough money so that a player would get eliminated, but even with this, it is unlikeley that a game will ever end.
       change <- 200
       action <- "Passed GO"
      } else if (space_type == "Income Tax") {
       change <- -200
       action <- "Paid Income Tax"
      } else if (space_type == "Chance" || space_type == "Community Chest") { #space if chance or chest
        # Random effect from card
        card_value <- sample(c(-100, -50, 0, 50, 100, 200), 1) #1 random value from those numbers
        change <- card_value #either add 200, -100, etc to player money count
        action <- ifelse(card_value >= 0, "Card gain", "Card loss") 
      } else if (space == "Go To Jail") {
        positions[player] <- 10  # Send to Jail
        action <- "Go to Jail"
      } else {
        action <- "Normal move" 
      }

      money[player] <- money[player] + change #money count updates each turn
      turns_alive[player] <- turns_alive[player] + 1 #adding 1 turn alive each turn

      # Log this turn
      log <- rbind(log, data.frame(
        Turn = turn,
        Player = player,
        Action = paste(action, "-", space),
        Money = money[player]
      ))

      # Eliminate if bankrupt
      if (money[player] <= 0) { #if money is equal than or less than 0
        eliminated[player] <- TRUE #eliminates the player
        log <- rbind(log, data.frame(
          Turn = turn,
          Player = player,
          Action = "Bankrupt!",
          Money = money[player]
        ))
      }
    }

    # Stop if only one player is left
    if (sum(!eliminated) <= 1) break
  }

  return(list(log = log, final_money = money, eliminated = eliminated, turns = turns_alive))
} #return stuff we need 

result <- simulate_economy_game(players = 4, max_turns = 4000)

# Show log of actions
head(result$log, 100) #used this to make sure that money was actually going up/down

# Final Money and Elimination Status
data.frame(
  Player = 1:4,
  Money = result$final_money,
  Eliminated = result$eliminated,
  TurnsSurvived = result$turns
)

library(ggplot2)

ggplot(result$log, aes(x = Turn, y = Money, color = factor(Player))) +
  geom_line(size = 1) +
  labs(title = "Player Money Over Time Without Property Ownership or Free Parking",
       x = "Turn", y = "Money ($)", color = "Player") +
  theme_minimal()
```

Money over time for a full game: 

In this game, we observed the performance of four players across 4000 turns. We used so many turns to give them a chance to eliminate themselves but the part of the game that gives them the most money (passing go) was changed in an effort to control the economy. In this version, you only got money if you landed on go instead of passing it. Even with this change in the rules, it seemed like the game would never end. This is because the money taking actions (tax / bad chance / bad chest) were not common enough to outweigh the money gaining actions. In this simulation though, there is noticeable variation in the money count as the game went on. Although, each player has a positive trend line, indicating that the game never would have ended. 



```{r, echo=FALSE}
set.seed(1)

#Prices and rent from monopoly spaces
monopoly_board$Rent <- c(NA, 2, NA, 4, NA, NA, 6, NA, 6, 8, NA, 10, NA, 10, 12, NA, 14, NA, 14, 16, NA, 18, NA, 18, 20, NA, 22, 22, NA, 24, NA, 26, 26, NA, 28, NA, NA, 35, NA, 50)

monopoly_board$Price <- c( NA, 60, NA, 60, NA, NA, 100, NA, 100, 120, NA, 140, NA, 140, 160, NA, 180, NA, 180, 200, NA, 220, NA, 220, 240, NA, 260, 260, NA, 280, NA, 300, 300, NA, 320, NA, NA, 350, NA, 400)
monopoly_board$Owner <- NA #starts so that nobody owns any properties from the start

#HAD TO REMOVE GETTING PAID FROM GO FEATURE, OTHERWISE PLAYERS WOULD NOT GET ELIMINATED

#Playing monopoly while buying property, but no free parking yet
simulate_game_with_ownership <- function(players = 4, max_turns = 500) {
  positions <- rep(0, players) #all explained above
  money <- rep(1500, players)
  eliminated <- rep(FALSE, players)
  owned_properties <- vector("list", players)  #List of empty vectors
  log <- data.frame()

  monopoly_board$Owner <- NA  # resets ownership

  for (turn in 1:max_turns) {
    for (p in 1:players) {
      if (eliminated[p]) next

      roll <- sum(sample(1:6, 2, replace = TRUE))
      positions[p] <- (positions[p] + roll) %% 40
      pos <- positions[p] + 1
      space <- monopoly_board[pos, ]

      action <- "Moved"
      change <- 0

      if (space$Type == "Go To Jail") {
        positions[p] <- 10
        action <- "Sent to Jail"
      } else if (space$Type == "Income Tax") {
        change <- -200
        money[p] <- money[p] + change #takes away money from player
        action <- "Paid Income Tax"
      } else if (space$Type == "Luxury Tax") {
        change <- -100
        money[p] <- money[p] + change #takes away money from player
        action <- "Paid Luxury Tax"
      } else if (space$Type == "Chance" || space$Type == "Community Chest") { #explained above
        change <- sample(c(-100, -50, 0, 50, 100), 1)
        money[p] <- money[p] + change #takes away or adds money to players balance
        action <- "Drew Card"
      } else if (space$Type == "Property") {
        if (is.na(space$Owner)) {
          # Try to buy property
          if (money[p] >= space$Price) {
            money[p] <- money[p] - space$Price
            monopoly_board$Owner[pos] <- p
            owned_properties[[p]] <- c(owned_properties[[p]], pos)  # Update player's owned properties
            action <- paste("Bought", space$Name) #action is bought x/y/z, etc
          }
        } else if (space$Owner != p) {
          # Pay rent if another player owns the property
          rent <- space$Rent
          money[p] <- money[p] - rent
          owner_id <- space$Owner
          if (!eliminated[owner_id]) {
            money[owner_id] <- money[owner_id] + rent
          }
          action <- paste("Paid rent to P", owner_id)
        }
        
      }

      # Log turn
      log <- rbind(log, data.frame(Turn = turn, Player = p, Position = pos, Action = action, Money = money[p]))

      # Check for bankruptcy
      if (money[p] <= 0) {
        eliminated[p] <- TRUE
        monopoly_board$Owner[monopoly_board$Owner == p] <- NA  # properties go back to bank
        owned_properties[[p]] <- integer(0)  # Clear owned properties for eliminated player
        log <- rbind(log, data.frame(Turn = turn, Player = p, Position = pos, Action = "Bankrupt", Money = 0))
      }

      if (sum(!eliminated) == 1) break
    }
    if (sum(!eliminated) == 1) break
  }

  remaining <- which(!eliminated)
  winner <- if (length(remaining) == 1) remaining else NA

  return(list(
    winner = winner,
    owned_properties = owned_properties,
    log = log
  ))
}

# Simulate multiple games
simulate_multiple_games <- function(n = 200, players = 4) {
  win_counts <- matrix(0, nrow = 40, ncol = 1)  # Track wins for each property
  colnames(win_counts) <- "WinsWithThisProperty"

  # Run 'n' games
  for (i in 1:n) {
    game <- simulate_game_with_ownership(players)
    if (!is.na(game$winner)) {
      # Get properties owned by the winner
      props <- game$owned_properties[[game$winner]]
      if (length(props) > 0) {
        win_counts[props] <- win_counts[props] + 1  # Increment win count for each owned property
      }
    }
  }

  result <- monopoly_board
  result$WinsWithThisProperty <- win_counts  # Add the win count to monopoly_board data
  return(result)
}

# Run multiple simulations
ownership_stats <- simulate_multiple_games(n = 200)



library(ggplot2)

ggplot(ownership_stats[ownership_stats$Type == "Property", ], 
       aes(x = reorder(Name, -WinsWithThisProperty), y = WinsWithThisProperty, fill = Color)) +
  geom_col() +
  scale_fill_manual(values = monopoly_colors) +
  labs(title = "Which Properties Are Most Often Owned by Winners Without Free Parking?",
       x = "Property", y = "Games Won with Property Owned") +
  theme(axis.text.x = element_text(angle = 90, size = 8),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") 

names(ownership_stats)[8] <- "WinsWithThisProperty" #changed the column name because there was an error in naming?
```

Which properties are most often owned by winners without free parking? 

The top 5 properties that are most owned by winners in highest to lowest are St. Charles Place, States Avenue, Vermont Avenue, Connecticut Avenue, and Tennessee Avenue all game won a little bit over 60. The 5 lowest properties from highest to lowest are Boardwalk, Indiana Avenue, North Carolina Avenue, Park Place, and Pennsylvania Avenue.  From this data we suggest owning the first 5 properties listed to have the best chance of winning the game of monopoly when free parking is not involved. 

```{r free parking, echo=FALSE}
set.seed(5)

#HAD TO REMOVE GETTING PAID FROM GO FEATURE, OTHERWISE PLAYERS WOULD NOT GET ELIMINATED

simulate_game_with_free_parking <- function(players = 4, max_turns = 1000) {
  free_parking <- 0 #free parking starts at 0
  positions <- rep(0, players) #all explained above
  money <- rep(1500, players)
  eliminated <- rep(FALSE, players)
  owned_properties <- vector("list", players)  #List of empty vectors
  log <- data.frame()

  monopoly_board$Owner <- NA  # resets ownership

  for (turn in 1:max_turns) {
    for (p in 1:players) {
      if (eliminated[p]) next

      roll <- sum(sample(1:6, 2, replace = TRUE))
      positions[p] <- (positions[p] + roll) %% 40
      pos <- positions[p] + 1
      space <- monopoly_board[pos, ]
      
      if (pos == 21) {
      money[p] <- money[p] + free_parking
      action <- paste("Landed on Free Parking, collected", free_parking)
      free_parking <- 0
     }

      action <- "Moved"
      change <- 0

      if (space$Type == "Go To Jail") {
        positions[p] <- 10
        action <- "Sent to Jail"
      } else if (space$Type == "Luxury Tax") {
        change <- -100
        money[p] <- money[p] + change
        free_parking <- free_parking - change  #have to do minus because change is already negative
        action <- "Paid Luxury Tax"
      } else if (space$Type == "Income Tax") {
        change <- -200
        money[p] <- money[p] + change
        free_parking <- free_parking - change  #have to do minus because change is already negative
        action <- "Paid Income Tax"
      } else if (space$Type == "Chance" || space$Type == "Community Chest") { #explained above
        change <- sample(c(-100, -50, 0, 50, 100), 1)
        money[p] <- money[p] + change
        if (change < 0) { #if change is less than zero, then pay to free parking
        free_parking <- free_parking - change  #add to Free Parking
      }
        action <- "Drew Card"
      } else if (space$Type == "Property") {
        if (is.na(space$Owner)) {
          # Try to buy property
          if (money[p] >= space$Price) {
            money[p] <- money[p] - space$Price
            monopoly_board$Owner[pos] <- p
            owned_properties[[p]] <- c(owned_properties[[p]], pos)  # Update player's owned properties
            action <- paste("Bought", space$Name) #action is bought x/y/z, etc
          }
        } else if (space$Owner != p) {
          # Pay rent if another player owns the property
          rent <- space$Rent
          money[p] <- money[p] - rent
          owner_id <- space$Owner
          if (!eliminated[owner_id]) {
            money[owner_id] <- money[owner_id] + rent
          }
          action <- paste("Paid rent to P", owner_id)
        }
      }

      # Log turn
      log <- rbind(log, data.frame(Turn = turn, Player = p, Position = pos, Action = action, Money = money[p]))

      # Check for bankruptcy
      if (money[p] <= 0) {
        eliminated[p] <- TRUE
        monopoly_board$Owner[monopoly_board$Owner == p] <- NA  # properties go back to bank
        owned_properties[[p]] <- integer(0)  # Clear owned properties for eliminated player
        log <- rbind(log, data.frame(Turn = turn, Player = p, Position = pos, Action = "Bankrupt", Money = 0))
      }

      if (sum(!eliminated) == 1) break
    }
    if (sum(!eliminated) == 1) break
  }

  remaining <- which(!eliminated)
  winner <- if (length(remaining) == 1) remaining else NA

  return(list(
    winner = winner,
    owned_properties = owned_properties,
    log = log
  ))
}

simulate_multiple_games_fp <- function(n = 200, players = 4) {
  win_counts <- matrix(0, nrow = 40, ncol = 1)  # Track wins for each property
  colnames(win_counts) <- "WinsWithThisProperty"

  for (i in 1:n) {
    game <- simulate_game_with_free_parking(players)
    if (!is.na(game$winner)) {
      # Get properties owned by the winner
      props <- game$owned_properties[[game$winner]]
      if (length(props) > 0) {
        win_counts[props] <- win_counts[props] + 1  # Increment win count for each owned property
      }
    }
  }

  result <- monopoly_board
  result$WinsWithThisProperty <- win_counts  # Add the win count to monopoly_board data
  return(result)
}

# Run multiple simulations
ownership_stats_fp <- simulate_multiple_games_fp(n = 200)

ggplot(ownership_stats_fp[ownership_stats_fp$Type == "Property", ], 
       aes(x = reorder(Name, -WinsWithThisProperty), y = WinsWithThisProperty, fill = Color)) +
  geom_col() +
  scale_fill_manual(values = monopoly_colors) +
  labs(title = "Which Properties Are Most Often Owned by Winners With Free Parking",
       x = "Property", y = "Games Won with Property Owned") +
  theme(axis.text.x = element_text(angle = 90, size = 8),
        plot.title = element_text(hjust = 0.5),
        legend.position = "none") 


```

Which properties are most often owned by winners when free parking is involved? 

The top 5 properties that are most owned by winners in highest to lowest are Tennesse Avenue, Vermont Avenue, States Avenue, St. Charles Place, and Baltic Avenue. The 5 lowest Properties from highest to lowest are Virginia Avenue, New York Avenue, Pennsylvania Avenue, Connecticut Avenue and Boardwalk. When free parking is involved, we suggest trying to own the top 5 properties. Interestingly enough, St. Charles, States, Tennesse, and Vermont were in the top 5 for both free parking and no free parking. Even crazier, however, is the fact that Connecticut was in the top 5 without free parking but in the bottom 5 with it. This could simply be down to chance in our simulation, but there might be some more reasoning behind it. 




```{r, echo=FALSE}
set.seed(5)

simulate_game_length <- function(n=200, players=4){
  game_length <- matrix(0,nrow = n, ncol = 1)
  colnames(game_length) <- "Length of Game"
  
  for (i in 1:n) {
    game <- simulate_game_with_free_parking(players)
    game_length[i] <- max(game$log$Turn)
  }
  return(game_length)
}

lengths <- as.numeric(simulate_game_length(n = 500))

summary(lengths)

df <- data.frame(values = lengths)

ggplot(df, aes(x=values))+
  geom_histogram(bins=50)
```

```{r, echo=FALSE}
set.seed(5)

simulate_game_no_bank <- function(players = 4, max_turns =1000) {
  free_parking <- 0 #free parking starts at 0
  positions <- rep(0, players) #all explained above
  money <- rep(1500, players)
  eliminated <- rep(FALSE, players)
  owned_properties <- vector("list", players)  #List of empty vectors
  log <- data.frame()

  monopoly_board$Owner <- NA  # resets ownership

  for (turn in 1:max_turns) {
    for (p in 1:players) {
      if (eliminated[p]) next

      roll <- sum(sample(1:6, 2, replace = TRUE))
      positions[p] <- (positions[p] + roll) %% 40
      pos <- positions[p] + 1
      space <- monopoly_board[pos, ]
      
      if (pos == 21) {
      money[p] <- money[p] + free_parking
      action <- paste("Landed on Free Parking, collected", free_parking)
      free_parking <- 0
     }

      action <- "Moved"
      change <- 0

      if (space$Type == "Go To Jail") {
        positions[p] <- 10
        action <- "Sent to Jail"
      } else if (space$Type == "Luxury Tax") {
        change <- -100
        money[p] <- money[p] + change
        free_parking <- free_parking - change  #have to do minus because change is already negative
        action <- "Paid Luxury Tax"
      } else if (space$Type == "Income Tax") {
        change <- -200
        money[p] <- money[p] + change
        free_parking <- free_parking - change  #have to do minus because change is already negative
        action <- "Paid Income Tax"
      } else if (space$Type == "Chance" || space$Type == "Community Chest") { #explained above
        change <- sample(c(-100, -50, 0, 50, 100), 1)
        money[p] <- money[p] + change
        if (change < 0) { #if change is less than zero, then pay to free parking
        free_parking <- free_parking - change  #add to Free Parking
      }
        action <- "Drew Card"
      } else if (space$Type == "Property") {
        if (is.na(space$Owner)) {
          # Try to buy property
          if (money[p] >= space$Price) {
            money[p] <- money[p] - space$Price
            free_parking <- free_parking + space$Price
            monopoly_board$Owner[pos] <- p
            owned_properties[[p]] <- c(owned_properties[[p]], pos)  # Update player's owned properties
            action <- paste("Bought", space$Name) #action is bought x/y/z, etc
          }
        } else if (space$Owner != p) {
          # Pay rent if another player owns the property
          rent <- space$Rent
          money[p] <- money[p] - rent
          owner_id <- space$Owner
          if (!eliminated[owner_id]) {
            money[owner_id] <- money[owner_id] + rent
          }
          action <- paste("Paid rent to P", owner_id)
        }
      }

      # Log turn
      log <- rbind(log, data.frame(Turn = turn, Player = p, Position = pos, Action = action, Money = money[p]))

      # Check for bankruptcy
      if (money[p] <= 0) {
        eliminated[p] <- TRUE
        monopoly_board$Owner[monopoly_board$Owner == p] <- NA  # properties go back to bank
        owned_properties[[p]] <- integer(0)  # Clear owned properties for eliminated player
        log <- rbind(log, data.frame(Turn = turn, Player = p, Position = pos, Action = "Bankrupt", Money = 0))
      }

      if (sum(!eliminated) == 1) break
    }
    if (sum(!eliminated) == 1) break
  }

  remaining <- which(!eliminated)
  winner <- if (length(remaining) == 1) remaining else NA

  return(list(
    winner = winner,
    owned_properties = owned_properties,
    log = log
  ))
}


simulate_game_length_no_bank <- function(n=200, players=4){
  game_length <- matrix(0,nrow = n, ncol = 1)
  colnames(game_length) <- "Length of Game"
  
  for (i in 1:n) {
    game <- simulate_game_no_bank(players)
    game_length[i] <- max(game$log$Turn)
  }
  return(game_length)
}

lengths_no_bank <- as.numeric(simulate_game_length_no_bank(n = 100))

summary(lengths_no_bank)

df_no_bank <- data.frame(values = lengths_no_bank)

ggplot(df_no_bank, aes(x=values))+
  geom_histogram(bins=100)
```

Analysis for how long games typically last: 

Our initial simulation was a sample of 500 games that included jail, free parking, and bank mechanics. The maximum number of turns allowed by the simulation was 1000. On average, these games lasted 101 turns and had a median of 61. The shortest game was 19 turns and the longest was a set of outliers at 1000 turns. In the second simulation, jail and free parking were included and all money paid to the bank instead went to free parking. This led to considerably longer games. In a sample of 100, the mean was 698 and the median was at the turn limit of 1000. The shortest game in this sample was 26 turns. Increasing the turn limit was not feasible with our resources. It was expected that adding free parking would increase the length of games, but we did not think it would be by this much. Without free parking, the money essentially “disappeared” from the game if a player lost it to tax or a card. But with free parking, this money was always in circulation and inevitably was going to end up in the hands of a player. At this point, for the games that did end, it was essentially luck that the same player landed on free parking repeatedly while the others did not. 

 