---
title: "Super Awesome Project Template"
output: word_document
date: "2025-04-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Luke Olson
1. Rules
Starting Cash
- Every player begins with $1,500 to start, and once you're out of liquid cash you lose.
Standard dice roll
- Player moves forward the number of spaces shown on two six sided dice. 
Rolling doubles
- Player rolls doubles (same number on both dice) and gets another turn. 
Three consecutive doubles
- If a player rolls doubles three times in a row, they go directly to jail. 
Passing Go
- If a player passes "Go" they collect $200 from the bank.
Chance Cards
- Certain board spaces have chance cards on them which instruct the player to move to a different space, or pay/earn money. They can send players to jail, Go, or various properties. 
Community Chest Cards
- Certain board spaces have community chest cards on them which instruct the player to move to a different space, pay/earn money, or get out of jail free card. 
Go to jail space
- Landing on "Go to jail" space sends the player directly to jail without collecting $200.
In jail movement
- the player can roll doubles to get out of jail, use the "get out of jail free" card, or pay $50. 

```{r Student1}

```


## Owen Schuler

```{r student2}

```


## Caden Rummel


```{r student3}

```



## Landen Frye

```{r student4}
2+2
```
