---
title: "Super Awesome Project Template"
output: word_document
date: "2025-04-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Luke Olson
1. Rules
Starting Cash
- Every player begins with $1,500 to start, and once you're out of liquid cash you lose.
Standard dice roll
- Player moves forward the number of spaces shown on two six sided dice. 
Rolling doubles
- Player rolls doubles (same number on both dice) and gets another turn. 
Three consecutive doubles
- If a player rolls doubles three times in a row, they go directly to jail. 
Passing Go
- If a player passes "Go" they collect $200 from the bank.
Chance Cards
- Certain board spaces have chance cards on them which instruct the player to move to a different space, or pay/earn money. They can send players to jail, Go, or various properties. 
Community Chest Cards
- Certain board spaces have community chest cards on them which instruct the player to move to a different space, pay/earn money, or get out of jail free card. 
Go to jail space
- Landing on "Go to jail" space sends the player directly to jail without collecting $200.
In jail movement
- the player can roll doubles to get out of jail, use the "get out of jail free" card, or pay $50. 
Buying/Landing on properties
- When you land on a property that hasn't been bought already, you are able to buy it if desired. If you land on a property that another player owns, you have to pay them an amount based on the property and houses on it. 

```{r Student1}
#2. Let's Get Moving

library(tidyverse)

#Creating the board
monopoly_board = tibble (position = 0:39, name = c("Go", "Mediterranean Avenue", "Community Chest", "Baltic Avenue", "Income Tax", "Reading Railroad", "Oriental Avenue", "Chance", "Vermont Avenue", "Connecticut Avenue", "Jail / Just Visiting", "St. Charles Place", "Electric Company", "States Avenue", "Virginia Avenue", "Pennsylvania Railroad", "St. James Place", "Community Chest", "Tennessee Avenue", "New York Avenue", "Free Parking", "Kentucky Avenue", "Chance", "Indiana Avenue", "Illinois Avenue", "B&O Railroad", "Atlantic Avenue", "Ventnor Avenue", "Water Works", "Marvin Gardens", "Go to Jail", "Pacific Avenue", "North Carolina Avenue", "Community Chest", "Pennsylvania Avenue", "Short Line", "Chance", "Park Place", "Luxury Tax", "Boardwalk"))

#settings for the simulation
n_players = 4

```


## Owen Schuler

```{r student2}

```


## Caden Rummel


```{r student3}

```



## Landen Frye

```{r student4}
2+2
```
